Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
net mets

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals, importance of individual layers, and the similarity of
different layers. To measure the role of individuals, we calculated degree
centrality and graph strength. Degree centrality is the number of direct
connections an individual has to other individuals in a network layer. Graph
strength is the degree weighted by the strength of association, in this case
SRI, in each layer-specific season and land cover context. Extending degree
centrality, we calculated multidegree, the sum of degree centrality of
individuals across layers, and neighbourhood, the sum of unique neighbours to
each individual across layers [@Berlingerio_2012; @Kivela_2014]. We evaluated
the relevance and redundancy of layers by combining the multidegree and
neighbourhood to calculate layer relevance and connective redundancy. Layer
relevance is the proportion of neighbours present in each layer compared to the
neighbourhood for each individual and connective redundancy is the proportion of
neighbours repeated in multiple layers, and [@Berlingerio_2012]. Finally, we
calculated the similarity of layers between seasons, across land cover classes
(e.g. summer open compared to winter open) using the Pearson correlation
coefficient [@Brodka_2018]. Network metrics were calculated using the R packages
`igraph` [@Csardi_2006], `asnipe` [@Farine_2019], `spatsoc`
[@Robitaille_2019] and `data.table` [@Dowle_2019].

@@

>>>>

We used a series of metrics to characterize the multilayer networks, focusing on
the role of individuals within and across layers, and the similarity of
different layers. To measure the role of individuals within layers, we
calculated degree centrality and graph strength. Degree centrality is the number
of direct connections an individual has to other individuals in a network layer.
Graph strength is the degree weighted by the strength of association, in this
case SRI, in each layer. Extending degree centrality, we calculated multidegree,
the sum of degree centrality of individuals across layers  [@Berlingerio_2012;
@Kivela_2014]. <!--We evaluated the relevance and redundancy of layers by
combining the multidegree and neighbourhood to calculate layer relevance and
connective redundancy. Layer relevance is the proportion of neighbours present
in each layer compared to the neighbourhood for each individual and connective
redundancy is the proportion of neighbours repeated in multiple layers, and
[@Berlingerio_2012].--> Finally, we measured the similarity of layers by
calculating edge overlap. Edge overlap is defined as the proportion of edges
present in each network layer out of all observed edges  [@Battiston_2014].
<!--between seasons, across land cover classes (e.g. summer open compared to
winter open) using the Pearson correlation coefficient [@Brodka_2018].-->
Network metrics were calculated using the R packages `igraph` [@Csardi_2006],
`asnipe` [@Farine_2019], `spatsoc` [@Robitaille_2019] and `data.table`
[@Dowle_2019].

@@

<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
